Interval Probability for Fuzzy Quantum Theories

### 2016-06-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} updating...

%%%%%
\subsection{Measuring Probabilities: Buffon's Needle Problem}

@@

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
between the additivity property of Kolmogorov probabilities 
\[
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
\]
and its quantum counterpart 
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
maps a linear space to its projection operator. In the Dempster-Shafer
theory, the additivity property is relaxed such that $\delta\left(E_{1},E_{2}\right)\ge0$
for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
is then analog to $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute.

Interestingly, this theory discussed the relation between non-commuting
subspaces while the real-valued quantum probability measures in definition~\ref{def:QuantumProbabilitySpace}
only depend on orthogonal (or commuting) subspaces. In order to understand
the intuition, let's go through the simplest example.

\begin{example}{[}Two-qubit quantum probability space{]} Consider
a two-qubit Hilbert space with the following subspaces:
\begin{eqnarray*}
S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
\end{eqnarray*}
 Then, their projection and non-additivity operators are 
\begin{eqnarray*}
\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
\end{eqnarray*}
We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
are
\begin{eqnarray*}
\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
\end{eqnarray*}
and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
However, I still don't have much intuition on why the probabilities
should have what kind of relations?\qed\end{example}

>>>>

%%%%%
\subsection{Measuring Probabilities: Buffon's Needle
Problem\label{subsec:Measuring-Probabilities:-Buffon}}

@@

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas started from
the additivity property of Kolmogorov probabilities 
\begin{equation}
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0\label{eq:Kolmogorov}
\end{equation}
which is intuitive because the relative frequencies of disjoint events
should be additive if the measurement is accurate. While $\delta\left(E_{1},E_{2}\right)$
is always zero for Kolmogorov probabilities, the additivity property
of the Dempster-Shafer theory is relaxed to $\delta\left(E_{1},E_{2}\right)\ge0$
for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
for the upper probability or plausibility. This modification is also
intuitive because the imprecision of whether an event happens or not
is taken into account, but we can still decide whether an instance
belongs to different events concurrently.

Vourdas observed that equation (\ref{eq:Kolmogorov}) is similar to
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear subspaces, and $\Pi$
maps a linear subspace to its projection operator. After apply the
Born rule on both sides, we get an equation about the probabilities
\begin{equation}
\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ .}\label{eq:quantum-additivity}
\end{equation}
Given the density matrix~$\rho$, the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is then analog to the sign of $\delta\left(E_{1},E_{2}\right)$ since
the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is not always zero. Vourdas then considered the pair $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
and $\Tr\left(\rho\Pi\left(S_{2}\right)\right)$ are lower or upper
probabilities depending on the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$.
Although Vourdas' idea is clear, the approach does not exactly fit
the idea. First, when we measure a physical quantity, we consider
the eigenspaces of an observable which always commute. According to
Vourdas' definition, $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
is then always an Kolmogorov probability within one measurement process.
Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
consider the following two-qubit example.

\begin{example}[Two-qubit quantum probability space] Consider
a two-qubit Hilbert space with the following subspaces:
\begin{eqnarray*}
S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
\end{eqnarray*}
We can implement the first qubit by the spin of a particle and the
second qubit in path

 Then, their projection and non-additivity operators are 
\begin{eqnarray*}
\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
\end{eqnarray*}
We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
are
\begin{eqnarray*}
\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
\end{eqnarray*}
and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
However, I still don't have much intuition on why the probabilities
should have what kind of relations?\qed\end{example}
